\bf Supervised Tensor Decomposition with Covariates on Multiple Modes

### 2020-09-02 tensor_regress/jasa-latexsource/tensor-jasa.tex
diff
update

\if1\blind
{
  \title{\bf Exponential Family Tensor Regression with Covariates on Multiple Modes}
  \author{Jiaxin Hu, Zhuoyan Xu, and Miaoyan Wang\\
    Department of Statistics, University of Wisconsin-Madison}
  \maketitle
} \fi

@@

\bigskip
\begin{abstract}
We consider the problem of tensor-response regression given covariates on multiple modes. Such data problems arise frequently in applications such as neuroimaging, network analysis, and spatial-temporal modeling. We propose a new family of tensor response regression models that incorporate covariates, and establish the theoretical accuracy guarantees. Unlike earlier methods, our estimation allows high-dimensionality in both the tensor response and the covariate matrices on multiple modes. An efficient alternating updating algorithm is further developed. Our proposal handles a broad range of data types, including continuous, count, and binary observations. Through simulation and applications to two real datasets, we demonstrate the outperformance of our approach over the state-of-art.
\end{abstract}

@@

\begin{figure*}[t]
\begin{center}
\includegraphics[width=16cm]{demo.pdf}
\end{center}
\caption{Examples of tensor response regression model with covariates on multiple modes. (a) Network population model. (b) Spatial-temporal growth model. }\label{fig:intro1}
\end{figure*}

>>>>

\if1\blind
{
  \title{\bf Supervised Tensor Decomposition with Covariates on Multiple Modes}
  \author{Jiaxin Hu, Zhuoyan Xu, and Miaoyan Wang\\
    Department of Statistics, University of Wisconsin-Madison}
  \maketitle
} \fi

@@

\bigskip
\begin{abstract}
We consider the problem of supervised tensor decomposition given covariates on multiple modes. Such data problems arise frequently in applications such as neuroimaging, network analysis, and spatial-temporal modeling. We propose a new family of tensor response regression models that incorporate covariates, and establish the theoretical accuracy guarantees. Unlike earlier methods, our estimation allows high-dimensionality in both the tensor response and the covariate matrices on multiple modes. An efficient alternating updating algorithm is further developed. Our proposal handles a broad range of data types, including continuous, count, and binary observations. Through simulation and applications to two real datasets, we demonstrate the outperformance of our approach over the state-of-art.
\end{abstract}

@@

\begin{figure*}[t]
\begin{center}
\includegraphics[width=16cm]{new_introfigure1.pdf}
\end{center}
\caption{Examples of tensor response regression model with covariates on multiple modes. (a) Network population model. (b) Spatial-temporal growth model. }\label{fig:intro1}
\end{figure*}
